Reasoning About a Machine with Local Capabilities

### 2018-05-13 toplas/paper.tex
Fix some latex bugs in the definition of Cauchy sequences and such.
reformulated a sentence

  As described in \sectionname~\ref{sec:reasoning}, we use the FTLR (Theorem~\ref{thm:ftlr}) to reason about unknown code, so we use it to reason about $c_\adv$.
  With the standard region $\iota^{nwl,p}$ chosen for the adversary, it is easy to show that the $\readCond{}$ and $\writeCond{}$ holds for $c_\adv$ which gives us $c_\adv \in \stder(W)$ by the FTLR.
  In order to get \eqref{eq:g1:main-O-res}, we need to show that (a) the memory satisfies the world and (b) the register file is in the $\stdrr(W)$.
  We have defined the world, so there (almost) is a one-to-one correspondence between region and memory segment in the initial configuration, so (a) is easily shown.
  In order to show (b), we need to show $c_\stk \in \stdvr(W)$ and $c_{g1} \in \stdvr(W)$.
  The former follows easily from the choice of a $\iota^{pwl}$-region for the stack in $W$.
  In order to argue the latter, we basically have to argue that $c_{g1}$, the closure generator, respects the world $W$.
  This amounts to showing that the closures generated by \texttt{g1} also respect the invariants of $W$.
  The reasoning concerning variable $x$ follows that of \citet{Dreyer:jfp12}, so we will ignore it in the remainder of the proof and focus on the reasoning related to this low-level scenario. \lars{preceding sentence is unclear: what is $x$, what does ``this low-level scenario'' refer to ?}

@@

\label{app:cofe}
This is an excerpt from \citet{Birkedal:tutorial-notes} about c.o.f.e.'s.
\begin{definition}[o.f.e.] An \emph{ordered family of equivalence} (o.f.e) is a
  set and a family of equivalences $\left(X, \left( \nequal \right)_{n=0}^\infty
  \right)$ that satisfy the following properties: 
  \begin{itemize}
  \item $\nequal[0]$ is the total relation on $X$
  \item $\forall n \ldotp \forall x,y \in X \ldotp x \nequal[n+1] y \Rightarrow
    x \nequal y$
  \item $\forall x,y \in X \ldotp (\forall n\ldotp x \nequal y) \Rightarrow x = y$
  \end{itemize}
  We say that an o.f.e. $\left(X, \seqn{\nequal{n}}\right)$ is \emph{inhabited} if there
  exists an element $x \in X$.
\end{definition}

@@

\begin{definition}[Cauchy sequences and limits]
  \label{def:cauchy-sequence}
  Let $\left(X, \seqn{\nequal} \right)$ be an o.f.e. and $\seq{x}$ be a sequence of
  elements of $X$. Then $\seq{x}$ is a \emph{Cauchy sequence} if
  \begin{align*}
    \forall k \in \nats, \exists j \in \nats, \forall n \geq j, x_j \nequal{k} x_n
  \end{align*}
  or in words, the elements of the chain get arbitrarily close.

  An element $x \in X$ is the \emph{limit} of the sequence $\seq{x}$ if
  \begin{align*}
    \forall k \in \nats, \exists j \in \nats, \forall n \geq j, x \nequal{k} x_n.
  \end{align*}
  A sequence may or may not have a limit. If it has we say that the sequence
  \emph{converges}. The limit is necessarily unique in this case
  and we write $\lim_{n\to\infty}x_n$ for it.
\end{definition}

>>>>

  As described in \sectionname~\ref{sec:reasoning}, we use the FTLR (Theorem~\ref{thm:ftlr}) to reason about unknown code, so we use it to reason about $c_\adv$.
  With the standard region $\iota^{nwl,p}$ chosen for the adversary, it is easy to show that the $\readCond{}$ and $\writeCond{}$ holds for $c_\adv$ which gives us $c_\adv \in \stder(W)$ by the FTLR.
  In order to get \eqref{eq:g1:main-O-res}, we need to show that (a) the memory satisfies the world and (b) the register file is in the $\stdrr(W)$.
  We have defined the world, so there (almost) is a one-to-one correspondence between region and memory segment in the initial configuration, so (a) is easily shown.
  In order to show (b), we need to show $c_\stk \in \stdvr(W)$ and $c_{g1} \in \stdvr(W)$.
  The former follows easily from the choice of a $\iota^{pwl}$-region for the stack in $W$.
  In order to argue the latter, we basically have to argue that $c_{g1}$, the closure generator, respects the world $W$.
  This amounts to showing that the closures generated by \texttt{g1} also respect the invariants of $W$.
  We reason about the local variable $x$ in the closure in the same way \citet{Dreyer:jfp12} does it.
  We ignore $x$ in the remainder this proof sketch to focus on the parts of the proof related to the setting of the capability machine.

@@

\label{app:cofe}
This is an excerpt from \citet{Birkedal:tutorial-notes} about c.o.f.e.'s.
\begin{definition}[o.f.e.] An \emph{ordered family of equivalence} (o.f.e) is a
  set and a family of equivalences $\left(X, \left( \nequal \right)_{n=0}^\infty
  \right)$ that satisfy the following properties: 
  \begin{itemize}
  \item $\nequal[0]$ is the total relation on $X$
  \item $\forall n \ldotp \forall x,y \in X \ldotp x \nequal[n+1] y \Rightarrow
    x \nequal y$
  \item $\forall x,y \in X \ldotp (\forall n\ldotp x \nequal y) \Rightarrow x = y$
  \end{itemize}
  We say that an o.f.e. $\left(X, \seqn{\nequal[n]}\right)$ is \emph{inhabited} if there
  exists an element $x \in X$.
\end{definition}

@@

\begin{definition}[Cauchy sequences and limits]
  \label{def:cauchy-sequence}
  Let $\left(X, \seqn{\nequal} \right)$ be an o.f.e. and $\seq{x}$ be a sequence of
  elements of $X$. Then $\seq{x}$ is a \emph{Cauchy sequence} if
  \begin{align*}
    \forall k \in \nats, \exists j \in \nats, \forall n \geq j, x_j \nequal[k] x_n
  \end{align*}
  or in words, the elements of the chain get arbitrarily close.

  An element $x \in X$ is the \emph{limit} of the sequence $\seq{x}$ if
  \begin{align*}
    \forall k \in \nats, \exists j \in \nats, \forall n \geq j, x \nequal[k] x_n.
  \end{align*}
  A sequence may or may not have a limit. If it has we say that the sequence
  \emph{converges}. The limit is necessarily unique in this case
  and we write $\lim_{n\to\infty}x_n$ for it.
\end{definition}
